The process of retrieving schedule data from the Novasoftware web application

### 2016-04-18 paper/paper.tex
Minor fixes to paper, started writing README

	In the case of the high school I attend; the school provides a separate schedule for Tuesdays via an independent application. This inconvenience of using separate applications for different days further increases the relevance of extracting the Novasoftware data, in order to unify the two schedules into one. Also, when thinking about the implications of having access to this data I realized that it could be used for research purposes; analyzing the schedules of different schools and drawing conclusions from them.

>>>>

	In the case of the high school I attend; the school provides a separate schedule for Tuesdays via an independent application. This inconvenience of using separate applications for different days of the week further increases the relevance of extracting the Novasoftware data, in order to unify the two schedules into one. Also, when thinking about the implications of having access to this data I realized that it could be used for research purposes; analyzing the schedules of different schools and drawing conclusions from them.
